\documentclass{article}
\usepackage{fancyhdr}
\usepackage{color}
\usepackage{titlesec}
\usepackage[margin=0.5in]{geometry}
\usepackage{tabto}
\usepackage{tabularx}

\definecolor{TitleColor}{rgb}{0.0, 0.0, 0.5}
\definecolor{SectionColor}{rgb}{0.0, 0.0, 0.7}
\definecolor{SubsectionColor}{rgb}{0.0, 0.0, 0.8}

\titleformat{\section}{\normalfont\Large\bfseries\color{SectionColor}}{\thesection}{1em}{}[{\titlerule[2.0pt]}]
\titleformat{\subsection}{\normalfont\bfseries\color{SubsectionColor}}{\thesection}{1em}{}

\title{\normalfont\Large\bfseries\color{TitleColor}Sprint Report \#2}
\date{\normalfont\bfseries\color{TitleColor}\today}

\begin{document}

\maketitle

\section*{Team Overview}
\subsection*{Project}
\tab{ARM Cluster}

\subsection*{Members}
\begin{itemize}
	\item Andrew Hoover
	\item Samantha Kranstz
	\item Christine Sorensen
\end{itemize}

\subsection*{Sponsor}
\tab{Dr. Christer Karlsson}

\subsection*{Meeting Times}
\tab{Tuesdays and Thursdays at 1:00pm

\section*{Sprint Overview}
During this sprint, our team first decided to use the ODROID devices instead of Raspberry PIs based on our findings from sprint one. We roughly planned out our budget for ethernet cables, the switch, varius USB cables, power strips, and the devices themselves and extra memory for them. At this stage, we did not chose exactly what we would buy, but we narrowed our budget enough to know that the number of devices we could have without going over the limit set by our sponser was eight. Dr. Karlsson then ordered seven more ODroids, an eight port switch, eight ethernet cables, and one USB to RJ45 device to benchmark USB to ethernet speeds. We encountered an issue where the order was backordered, and we did not receive the devices until over two weeks laters. Once we did get them, we benchmarked the speed over ethernet between two devices through the switch, and the speed when one device was using a USB to RJ45 to connect to the switch. We also attempted to benchmark the direct connection between RJ45 on one device connected directly to the ethernet of another device, but found that we would need a crossover cable. We concluded our sprint by setting up all eight devices by installing MPI and giving them static IP addresses on the network over the switch.

\section*{Setback}
The seven ODROIDs ordered were actually backordered.  Therefore, they did not arrive until after sprint 2 was over. 

\section*{Deliverables}
\begin{itemize}
	\item Updated Design Document
	\item Budget
	\item Hardware Test
	\item Switch Benchmark
	\item Ethernet Benchmark
	\item USB to Ethernet Benchmark
	\item MPI Code
	\item Message-Passing Protocol
\end{itemize}

\section*{Activities}
\subsection*{Team}
\begin{itemize}
	\item Decided on using the ODROID
	\item Order ODROIDs and selected supplies
\end{itemize}

\subsection*{Andrew Hoover}
\begin{itemize}
	\item Benchmarked:
		\begin{itemize}
			\item Switch
			\item Ethernet
			\item USB to Ethernet
		\end{itemize}
	\item Tested hardware
	\item Tested MPI code on ODROIDS
\end{itemize}
\subsection*{Samantha Kranstz}
\begin{itemize}
	\item Researched supplies
	\item Finialized budget
	\item Researched patents and other clusters
\end{itemize}
\subsection*{Christine Sorensen}
\begin{itemize}
	\item Designed message-passing protocols
	\item Sampled MPI code
\end{itemize}

\subsection*{Work that is carried over into Sprint 3 is as follows:}
\begin{itemize}
	\item Design cluster
	\item Build cluster
	\item Benchmark cluster
	\item Test message-passing
\end{itemize}

\section*{Backlog}
\begin{itemize}
	\item Build the cluster
	\item Code for the cluster
	\item Benchmark the cluster
	\item Experiment with different topologies
	\item Create a new mode of communication
\end{itemize}

\section*{Goals}
\begin{itemize}
	\item Go to research symposium
	\item Prepare Design Fair
\end{itemize}

\end{document}
