\documentclass{article}
\usepackage{fancyhdr}
\usepackage{color}
\usepackage{titlesec}
\usepackage[margin=0.5in]{geometry}
\usepackage{tabto}
\usepackage{tabularx}

\begin{document}
\section*{Benchmark Log}
\subsection*{Testing}
Benchmark code was written that tested the length of time to add, multiply, divide, and sine two arrays consisting of 100,000 random floating point numbers that were generated in a seperate number generated program outputting numbers between one and one thousand. The code ran on all cores of the devices.

\subsection*{Results}
The PcDuino 8 was not working correctly so it was removed from our selection. This did not cause a huge effect in the project considering each PcDuino costs about \$160 and therefore was not a front runner in our experimentation.\newline

The Raspberry Pi 2B with 4 cores and the ODrioid 4xU with 8 cores were tested. The results were as follows:

\begin{center}

\begin{tabular}{ | l || l | l | l | l | }
\hline
\multicolumn{5}
{ |c| }{ Length of Time (seconds) } \\
\hline
Device & Addition & Multiplication & Division & Sine \\
\hline
ODroid 4xU & 29.925 & 31.341 & 37.032 & 227.40 \\
\hline
Raspberry Pi 2B & 221.645 & 221.034 & 297.204 & 1468.63 \\
\hline
\end{tabular}

\vspace{5mm}

\begin{tabular}{ | l || l | l | l | l | }
\hline
\multicolumn{5}
{ |c| }{ Gigaflops } \\
\hline
Device & Addition & Multiplication & Division & Sine \\
\hline
ODroid 4xU & 0.311 & 0.297 & 0.251 & 0.0410 \\
\hline
Raspberry Pi 2B & 0.0420 & 0.0421 & 0.0313 & 0.00634 \\
\hline
\end{tabular}

\vspace{5mm}

\begin{tabular}{ | l || l | l | l | l | }
\hline
\multicolumn{5}
{ |c| }{ Gigaflops per Dollar per Watts } \\
\hline
Device & Addition & Multiplication & Division & Sine \\
\hline
ODroid 4xU & 0.00028 & 0.000268 & 0.000226 & 0.0000369 \\
\hline
Raspberry Pi 2B & 0.0003 & 0.0003 & 0.000224 & 0.0000453 \\
\hline
\end{tabular}
\end{center}

\subsection*{Conclusion}
The Raspberry Pi 2B proved to be be better than the ODroid 4xU, however they were very close. We are inconclusive as to whick one will be used for the cluster. In the following Sprint 2, we will look into the ordering parts and our budget to make a choice as to which of the two single-board computers we will use.
\end{document}