\documentclass{article}
\usepackage{fancyhdr}
\usepackage{color}
\usepackage{titlesec}
\usepackage[margin=0.5in]{geometry}
\usepackage{tabto}
\usepackage{tabularx}

\definecolor{TitleColor}{rgb}{0.0, 0.0, 0.0}
\definecolor{SectionColor}{rgb}{0.3, 0.3, 0.3}
\definecolor{SubsectionColor}{rgb}{0.4, 0.4, 0.4}

\titleformat{\section}{\normalfont\Large\bfseries\color{SectionColor}}{\thesection}{1em}{}[{\titlerule[2.0pt]}]
\titleformat{\subsection}{\normalfont\bfseries\color{SubsectionColor}}{\thesection}{1em}{}

\title{\normalfont\Large\bfseries\color{TitleColor}Sprint Report \#5}
\date{\normalfont\bfseries\color{TitleColor}\today}

\begin{document}

\maketitle

\section*{Team Overview}
\subsection*{Project}
\tab{ARM Cluster}

\subsection*{Members}
\begin{itemize}
	\item Andrew Hoover
	\item Christine Sorensen
\end{itemize}

\subsection*{Sponsor}
\tab{Dr. Christer Karlsson}

\subsection*{Meeting Times}
\tab{Tuesdays and Thursdays at 1:00pm}
\subsection*{Work Times}
\tab{Tuesdays and Thursdays at 10:00am}

\section*{Sprint Overview}
\subsection*{Work for this sprint included:}
\begin{itemize}
	\item Designed new topologies.
	\begin{itemize}
		\item Used usb-to-ethernet cords to create these topologies.
		\item Created a 4 point and 8 point ring.
		\item Created a hypercube.
	\end{itemize}
	\item Created routing tabled for each ODROID.
	\begin{itemize}
		\item Seeked advice from Dr. Qiao.
		\item Debugged the errors of communicating.
	\end{itemize}
	\item Researched GPIO communication.
	\begin{itemize}
		\item Speed of the communication was benchmarked.
	\end{itemize} 
	\item MICS conference.
	\begin{itemize}
		\item Was accepted to the MICS conference.
		\item Began first draft of paper to deliver to MICS.
	\end{itemize}
	\item SDSMT Research Symposium
	\begin{itemize}
		\item Wrote abstract for our research to deliver to the SDSMT Research Symposium.
	\end{itemize}
\end{itemize}

\section*{Deliverables}
\begin{itemize}
	\item Design for the hypercube and ring topology.
	\item Routing tables for each of the ODROIDs.
	\item The cluster connected with new topology.
	\item Able to send bits over GPIO between ODroid devices.
	\item Acceptance into MICS.
	\item First draft of MICS paper.
	\item SDSMT Research Symposium abstract.
\end{itemize}

\section*{Activities}

\subsection*{Andrew Hoover}
\begin{itemize}
	\item Connected the cluster using the usb-to-ethernet cords.
	\item Designed the hypercube.
	\item Connected cluster into a ring and hypercube.
	\item Set new IP addresses to the ODROIDs.
	\item Debugged connection between the ODROIDs in new topology.
	\item Talked to faculty about networking and routing tables.
	\item Wrote routing tables.
	\item Debugged LINPACK to benchmark the new cluster connection.
	\item Edited sprint report.
\end{itemize}
\subsection*{Christine Sorensen}
\begin{itemize}
	\item Wrote SDSMT abstract.
	\item Began first draft of MICS paper.
	\item Designed the hypercube.
	\item Designed protocol for communication in the hypercube.
	\item Set new IP addresses to the ODROIDs.
	\item Updated documentation.
	\item Tested GPIO communication.
	\item Talked to faculty about networking and routing tables.
	\item Wrote routing tables.	
	\item Wrote initial sprint report.
\end{itemize}

\subsection*{Work that is carried over into Sprint 5 is as follows:}
\begin{itemize}
	\item Write MICS paper.
	\item Prepare presentation for SDSMT's Research Symposium.
	\item Prepare presentation for MICS.
	\item Benchmark the hypercube cluster.
	\item Prepare for client presentations.
\end{itemize}

\section*{Backlog}
\begin{itemize}
	\item MICS presentation.
	\item SDSMT Research Symnposium.
	\item Completed hypercube cluster.
	\item Conglomerate data results.
	\item Design Documentation.
	\item Design Fair.
\end{itemize}
\end{document}
